---
title: "p8105_hw5_jz3183"
author: "Jungang Zou"
date: "11/2/2019"
output: github_document
---

```{r set up, include = FALSE}
# knitr will run the chunk but not include the chunk in the final document
# copy from Jeff

# ensure reproductivity
set.seed(10)

# load library
library(tidyverse)
library(viridis)
library(ggridges)
library(patchwork)
library(rvest)

knitr::opts_chunk$set(
  # display the code in the code truck above its results in the final document
  echo = TRUE,
  # do not display any warning messages generated by the code
  warning = FALSE,
  # set the figure to be 8 x 6, and the proportion it takes to be 90%
  fig.width = 8,
  fig.height = 6, 
  out.width = "90%"
)

# setting a global options for continuous data color family and a different format to set discrete data to have a color family
options(
  ggplot2.countinuous.colour = "viridis",
  ggplot2.countinuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

# have a minimal theme and legends at the bottom
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

# Homework 5 for Data Science Course p8105

## Problem 1

First, we read the data.

```{r p1_read_data, collapse = TRUE}
# In this code chunk, we will read the dataset iris
iris_with_missing = 
  iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

# display
iris_with_missing
```

Then, we need to write 1 function to fill the missing values according to the following rules:

* For numeric variables, you should fill in missing values with the mean of non-missing values
* For character variables, you should fill in missing values with "virginica"

In the next code chunk, I write a function to fill the missing value and display the data.
```{r p1_functions, collapse = TRUE}
# in this code chunk, we write a function "fill_missing" and use "map_df" to fill the missing data. 
fill_missing = function(vec) {
  
  if (is.numeric(vec)) {
    vec = 
      vec %>% 
      replace_na(mean(vec[!is.na(vec)]))
  } else if (is.character(vec)) {
    vec = 
      vec %>% 
      replace_na("virginica")
  }
  vec
}

# fill the missing data
iris_without_missing <- map_df(.x = iris_with_missing, ~ fill_missing(.x))

# display
iris_without_missing
```


## Problem 2

In this problem, we need to firstly read datasets from local files according to the process:

* Start with a dataframe containing all file names; the list.files function will help
* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r p2_read_data, collapse = TRUE, message = FALSE}
# In this code chunk, we will read the datasets

# read the file names for all datasets
dataset_name = 
  list.files("./dataset_p2/data", pattern = "^.+_.+.csv$") %>% 
  as.data.frame() %>% 
  map_dfc(.x = ., ~paste("./dataset_p2/data", ., sep = "/")) %>%              # add path
  rename("file_name" = ".")

# display
dataset_name


# read dataset as a dataframe and create a variable "file_data" to save the data
nest_data = 
  dataset_name %>% 
  # create a variable named file_data to denote the nested data
  mutate("file_data" = purrr::map(.x = pull(., file_name), read_csv))        # read data
  
# display
nest_data  

# tidy the nest_data
df_p2 = 
  nest_data %>% 
  mutate(file_name = str_extract(file_name, "[conexp]{3}_[0-9]{2}")) %>%     # delete ".csv" in file names
  separate(file_name, into = c("arm", "subject_id"), sep = "_") %>%          # seperate filename into arm and id
  mutate(arm = str_replace(arm, "con", "control"), arm = str_replace(arm, "exp", "experimental")) %>% 
  #mutate(subject_id = as.numeric(subject_id)) %>%                            # convert id into numeric
  unnest(cols = "file_data")                                                  # unnest
  

# display
df_p2
```

After tidy the data, we will make a spaghetti plot showing observations on each subject over time:

```{r p2_spaghetti, echo = FALSE}
df_p2 %>% 
  pivot_longer(
    cols = week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  ) %>% 
  #filter(arm == "control") %>% 
  ggplot(aes(x = week, y = value, color = subject_id)) +
  geom_line(aes(x = week, y = value, group = subject_id)) +
  facet_grid(.~arm) +
  labs(
    title = "Spaghetti Plot for Arms in Differet Weeks",
    x = "Week",
    y = "Value",
    caption = "Data from URL: https://p8105.com/data/hw5_data.zip") +
  theme(plot.title = element_text(hjust = 0.5))
```

From the spaghetti graph, we may draw the conclusion that the values of control arm are nearly kept during 8 weeks. However, the values of experimental arm are increased during 8 weeks. This result may show that the experiment can make a difference during the time.